HBCC - ACC-Nirmala - FEATURECOUNTS - GRCh38 - CQN - Sparse Model

### 2020-01-31 cmc-rnaseq-de/HBCC_ACC-Nirmala_FEATURECOUNTS_GRCh38_CQN_Sparse.Rmd
verbose md filter

# Get genotype ids from synapse
GENOTYPE_ID = 'syn16816490'
ALL_USED_IDs = c(ALL_USED_IDs, GENOTYPE_ID)
GENOTYPE = downloadFile(GENOTYPE_ID) %>% 
  dplyr::select(Individual_ID, `SNP_report:Genotyping_Sample_ID`, `SNP_report:Exclude?`) %>% 
  dplyr::inner_join(ANCESTRY)
```

@@

                           data.frame(ensembl_gene_id = rownames(lcpm)[i], BIC = BIC(mdl))
                         }, 
                         lcpm, designMat, voomWeights, 
                         .parallel = F,
                         .paropts = list(.packages = c('dplyr')))
  return(modelBIC)
}

# vars.selected = selectCovarsToAdjust(phase1.covars, adjust.covars, 
#                                      COVARIATES, CQN.GENE_EXPRESSION$E, 
#                                      NEW.COUNTS, baseModelBIC)
# Function to select covariates in a step-wise regression fashion
selectCovarsToAdjust <- function(covarsToSelect, adjustCovars, covars, lcpm, cnt, baseModelBIC){

>>>>

# Get genotype ids from synapse
GENOTYPE_ID = 'syn16816490'
ALL_USED_IDs = c(ALL_USED_IDs, GENOTYPE_ID)
GENOTYPE = downloadFile(GENOTYPE_ID) %>% 
  dplyr::select(Individual_ID, `SNP_report:Genotyping_Sample_ID`, `SNP_report:Exclude?`) %>% 
  dplyr::inner_join(ANCESTRY) %>% 
  %>% 
  dplyr::filter(is.na(`SNP_report:Exclude?`)) #Remove excluded samples here because there are duplicate individuals
```

@@

                           data.frame(ensembl_gene_id = rownames(lcpm)[i], BIC = BIC(mdl))
                         }, 
                         lcpm, designMat, voomWeights, 
                         .parallel = F,
                         .paropts = list(.packages = c('dplyr')))
  return(modelBIC)
}
# Function to select covariates in a step-wise regression fashion
selectCovarsToAdjust <- function(covarsToSelect, adjustCovars, covars, lcpm, cnt, baseModelBIC){
